\begin{center}
\doublespacing
{\large \textbf{ACKNOWLEDGEMENTS}}
\end{center}

\onehalfspacing
%\singlespacing

%This thesis has become a reality with the kind support and help of many individuals. Each one of them have their pleasant impact on my personal and professional
%life. The impression that they had left on me will remain with me forever. I would like to take a moment to extend my sincere gratitude towards all of them.
%{\setstretch{1.17}
This thesis is the culmination of my journey of Ph.D which was just like climbing a high peak step by step accompanied with encouragement,
hardship, trust, and frustration. When I found myself at the top experiencing the feeling of fulfillment, I realized though only my name appears on
the cover of this thesis, a great many people have contributed to accomplish this huge task. 

Foremost, I want to offer this endeavour to \textbf{GOD Almighty} for the wisdom he bestowed upon me, the strength, peace of mind and good health, in order to finish
this research.

I would like to express my deepest gratitude towards my mentor and advisor Prof.\ Brajesh C. Choudhary for his constant guidance, overwhelming support and patience,
though mixed with occasional shouting.
His great insight into the subject has always been valuable whenever I found myself directionless. 
He has always understood my constraints and encouraged me to perform better. It was his faith and motivation that helped me in sustaining my efforts which many
a times did oscillate. I am really thankful to him for providing me the opportunity to be a part of one of the world's biggest high energy physics experiments.
He has also taught me the importance of being organized and having a professional attitude in work. 

I also wholeheartedly thank Prof.\ Debajyoti Choudhury who is solely responsible for creating and enhancing my interest in the theoretical aspect of high energy
physics. I consider myself blessed and privileged for his significant guidance during the initial years of my Ph.D life. He has always been available and guided me
with best of his knowledge whenever I needed his help during any stage of my research. 

I owe a sincere thanks to Dr.\ Varun Sharma with whom I have worked closely since the beginning of my Ph.D tenure. I am very grateful for his help and guidance
at both the fundamental and technical levels. His suggestions have always been of invaluable importance during each stage of my research work.   
I also thank Dr. Sushil Singh Chauhan for his fruitful suggestions and discussions during the final stages of this study.
My heartfelt thanks also goes to Dr.\ Daniele Del Re and Prof.\ Robert Brown for their thorough reviews and important suggestions which have played a vital role
in improving this analysis. A special thanks to Dr.\ Dinko Ferencek and Dr.\ Javier M.\ Duarte for their availability and providing a helping hand on the technical front.
A vote of thanks to all the members of CMS collaboration and the people involved in this analysis directly or indirectly.
I am also thankful to LHC Physics Center, Fermilab, USA for providing computational resources for this analysis.

I acknowledge the members of my advisory committee, Dr.\ Nivedita Deo and Dr.\ Supriya K.\ Kar for their valuable advice and suggestions.
I am truly obliged to Prof.\ Sanjay Jain, Head of the Department of Physics $\&$ Astrophysics, for providing adequate facilities and comfortable environment
in the department. I also thank Mr.\ Pradeep Kundra for handling the administrative matters properly.

My thanks and appreciations also go to all the members of Experimental High Energy Physics group at the University of Delhi, including
Prof.\ R.\ K.\ Shivpuri, Prof.\ Kirti Ranjan, Dr.\ Ashutosh Bhardwaj, Dr.\ Md. Naimuddin and Dr.\ Ashok Kumar.
I also thank all the members of India-CMS collaboration for their encouragement and support during the various meetings.  
A sincere thank to the Council of Scientific and Industrial Research (CSIR) for providing the fellowship in order to carry out this research. I also 
would want to thank DAE-DST (Govt.\ of India) and UGC for the financial support for international travels. 

I am highly indebted to my seniors and colleagues in the department, Dr.\ Sudha Ahuja, Dr.\ Varun Sharma, Dr.\ Arun Kumar, Dr.\ Ajay Kumar,
Dr.\ Daljeet Kaur, Dr. Shivali Malhotra, Dr.\ Ranjeet Dalal, Ramkrishan Sharma, Arjun Chettri, Kanwaljeet Singh Channey, Sumit Kesri, Zubair Ahmed Dar,
Ankit Gaur, Geetika Jain, Aashaq Hussain Shah, Mohit Gola, Priyanka Phogat, Probhjot Singh, Aman Phogat, Prajesh Sharma, Ashar, Rijwan, Chakaresh,
for their goodwill and constant encouragement. My appreciation also extends to the members of laboratory staff, Md.\ Yunus, Aamir Hussain and Atul, for
their innumberable help. 
 
This acknowledgement will never be complete without the mention of my bosom friends, Reena Ghadwal and Rachna Vats who have always loved me for who I am.
I can truly be myself when I am with them. Its Reena, who truly laid the first stone of my Ph.D journey. I will always be indebted to her for this. 

I revere the patronage and moral support extended with love, by my family (specially, my in-laws family), whose encouragement, support and patience
has made it possible  for me to complete this journey. I owe this success to my mother-in-law who has always understood me and cared for me like her
own daughter. I am truly grateful to my brother-in-law for supporting me and giving me the love and care of an elder brother.  
A big thank to my dear brother, Yogesh Singla who has always been my morale booster. 
My deep appreciations to Amit and Indu Goel for always being around. Much love to my nephew Naman Garg, for his innocent affections. 

It is impossible to acknowledge, in words, the unconditional love and support that I got from my husband during this journey. This thesis has become a reality only
because of his continuous efforts. He was always around at times when I thought it is
impossible to continue. He helped me to keep things in perspective. I greatly value his contribution and deeply appreciate his belief in me. 
My heart goes to my baby, my little girl Kriti for her selfless love and positivity that she brought in my life. She has truly been my lucky charm.
I appreciate her for abiding my ignorance and for the patience she showed during this time. 
%}

\vspace{0.1in}
\begin{flushright}
{\large Rocky Bala Garg}
\end{flushright}



